NumPy---Array Computation for Python

### 2020-01-04 paper.tex
Use two columns

\documentclass[fleqn,10pt]{wlscirep}

@@

\lstset{ %
  basicstyle=\ttfamily\footnotesize,  % size of fonts used for the code
  xleftmargin=2\parindent,
  breaklines=true,   % automatic line breaking only at whitespace
  captionpos=b,   % sets the caption-position to bottom
  commentstyle=\color{gray},  % comment style
  keywordstyle=\color{blue},  % keyword style
  stringstyle=\color{red},  % string literal style
  upquote=true  %straight single quotes (requires textcomp)
}

@@

\usepackage{lineno}
\linenumbers

>>>>

\documentclass[fleqn,10pt,twocolumn]{wlscirep}

@@

\lstset{ %
  basicstyle=\ttfamily\footnotesize,  % size of fonts used for the code
  xleftmargin=\parindent,
  breaklines=true,   % automatic line breaking only at whitespace
  captionpos=b,   % sets the caption-position to bottom
  commentstyle=\color{gray},  % comment style
  keywordstyle=\color{blue},  % keyword style
  stringstyle=\color{red},  % string literal style
  upquote=true  %straight single quotes (requires textcomp)
}

@@

\usepackage[switch]{lineno}
\linenumbers
